A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-11 paper.tex
merge

Now consider a classical field theory where the spacetime manifold is $M=\RR^n$ which is moreover translation-invariant. Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$. A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action is extended to an action of the super Lie algebra $\fA$. In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.

@@

In these paper we consider supersymmetric Yang--Mills theories in dimensions 2 through 10. In dimensions 3 through 10 these may be obtained by dimensional reduction of the following theories: 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills, 4d $\cN=1$ super Yang--Mills and 3d $\cN=1$ super Yang--Mills. First of all, these theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing. In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 thse depend on a choice of an orthogonal $\fg$-representation. We do not consider superpotential and mass terms in this paper. Moreover, as we are working perturbatively, we ignore all topological terms ($\theta$-terms).

@@

% \item  Context and literature on twists, including in the BV formalism.  There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).  Also at least a remark on the perspective in terms of coupling to twisted sugra.
% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
%\end{enumerate}}

>>>>

Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, which is moreover translation-invariant. Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$. A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action is extended to an action of the super Lie algebra $\fA$. In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.

@@

In these paper we consider supersymmetric Yang--Mills theories in dimensions 2 through 10. In dimensions 3 through 10 these may be obtained by dimensional reduction of the following theories: 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills, 4d $\cN=1$ super Yang--Mills and 3d $\cN=1$ super Yang--Mills. First of all, these theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing. In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation. We do not consider superpotential and mass terms in this paper. Moreover, as we are working perturbatively, we ignore all topological terms ($\theta$-terms).

@@
